Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s07_problempinning.tex
Further proof reading. Fixed \emph problem!

\begin{definition}
    A \dfn{multi-triangle-pin graph} is a body-hyperpin graph where each body is a triangle, meaning it is pinned in at most 3 places. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hyper-graphs, 1 and 2-dof can be characterized by $(2,4)$ and $(2,5)$ tightness respectively.
\end{definition}

@@

We can develop the notion of a canonical DR-plan for certain $(k,l)$ tightness conditions similar to the way we did in Section \ref{sec:DRP}.

@@

    All $(k,l)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$ tight case for bar and joint graphs discussed in Section \ref{sec:DRP}. This is due tot he fact that such $(k,l)$-tight graphs are matroidal and have a pebble game.
\end{remark}

@@

    For the multi-triangle pin graphs, we can do the same thing except we need to add a single triangle to one of the nodes to cause it to become isostatic.

    % For the 2-dof case, we can do something very similar, except instead of pinning a single body 2 times to a node, we can pin another body 2 times to a node. These can be the same node, and if it is the same node, we can find a wellconstrained DR-plan in quadratic time, we would just be doing the same thing as the 1-dof case.
\end{proof}

>>>>

\begin{definition}
    A \dfn{multi-triangle-pin graph} is a body-hyperpin graph where each body is a triangle, meaning it is pinned in at most 3 places. This is also represented as a hyper-graph where each pin is a vertex and each triangle represents a tri-hyperedge. For such hyper-graphs, 1 and 2-dof can be characterized by $(2,4)$ and $(2,5)$-tightness respectively.
\end{definition}

@@

We can develop the notion of a canonical DR-plan for certain $(k,l)$-tightness conditions similar to the way we did in Section \ref{sec:DRP}.

@@

    All $(k,l)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar and joint graphs discussed in Section \ref{sec:DRP}. This is due tot he fact that such $(k,l)$-tight graphs are matroidal and have a pebble game.
\end{remark}

@@

    For the multi-triangle pin graphs, we can do the same thing except we need to add a single triangle to one of the nodes to cause it to become isostatic.
    % Don't leave a blank line between last paragraph and end!
    % For the 2-dof case, we can do something very similar, except instead of pinning a single body 2 times to a node, we can pin another body 2 times to a node. These can be the same node, and if it is the same node, we can find a wellconstrained DR-plan in quadratic time, we would just be doing the same thing as the 1-dof case.
\end{proof}
